Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
tex

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	\vspace{-2.0em}
	\caption{
		%
		Comparison in robustness, training time cost, and recall@1 performance
		between our method and the state-of-the-art method (\ie, ``ACT'').
		%
		Our method (\ie, ``HM'') performs much better in all the three aspects.
		%
	}
	\label{fig:introplot}
\end{figure}

>>>>

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	%\vspace{-2.0em}
	\caption{
		%
		Comparison in Robustness, Training Cost, and Recall@1 Performance
		between Our Method (\ie, ``HM'') and the State-of-The-Art Method (\ie, ``ACT'').
		%
		Best viewed in color.
	}
	\label{fig:introplot}
\end{figure}
